A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-22 manuscript/supplemental.tex
added Tomas and Kate comments to SI

  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty. We began by constructing 100 ``true" networks with 50 consumer species, 50 resource species, and a connectance of 0.1. We ensured that each network had at least one link per consumer and per resource. For each network, we calculated the mean number of links per consumer, mean number of links per resource, and nestedness (NODF) as described in the main text. For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).

  Taking each ``true" network as a starting point, we then applied process uncertainty. The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution. As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred. The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive. The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$. If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network. As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network. For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF.

  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks. As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution. We also randomly selected the probability, $p$, of detecting each interaction. To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10. We created 100 detection-filtered networks for each process-filtered network (10000 per true network). For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF. Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.

  With each additional layer of uncertainty, the number of consumers and resources included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs). The connectance and number of links per consumer and per resource decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests). The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types. Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001). We note that these tests may reflect the large number of detection-filtered webs generated by our simulation. A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network. This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.

@@

        The absence of an interaction on a given day could be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

@@

        \begin{figure}[h!]
          \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$. The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$. Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
          Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
          \label{upper_limits}
          \begin{center}
          \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
          % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
          \end{center}
          \end{figure}

@@

    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial. In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:

@@

    \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
    The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:

@@

    Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :

@@

    According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}). Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:

@@

   The beta-binomial distribution is a conjugate distribution of the binomial distribution. This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution. We can re-write the posterior distribution of $\lambda$ as:

@@

    \noindent where the function $B$ is the beta function. The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.

    For interactions which were observed in at least one site ($k$\textgreater$0$), we can set the poseterior probability to 1 as long as the risk of a false positive is low. That is, when constructing a metaweb we can assume that an interaction observed at least once is truly feasible. The case study presented in the main text refers to a plant-galler network compiled by rearing galling insects obtained from galls; in each case, the plant-galler interaction definitely occurred and we are confident in the identification of both species involved (see \emph{Appendix S4} for details). Where the risk of false positives is higher (e.g., plant-pollinator networks where an observed flower visitor may not actually provide a pollination service), it may not be appropriate to assume $\lambda=$ wherever $k$\textgreater$0$. In such cases, we can model the posterior probabilities of observed interactions just as we do those that were not observed.

@@

      It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

      The \textbf{average} of $\lambda$ is: 
          \begin{equation}
            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
            \label{mean}
          \end{equation}

@@

      The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

        The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data. We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$. With some simple R code (function ``calculate\_parameters", \emph{Appendix S7}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63. Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S7}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026. Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance. We may also wish to calculate a credible interval (analogous to the frequentist confidence interval). This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S7}). In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).

        Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability that these two species do not interact''? Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The function ``samples\_for\_threshold" in \emph{Appendix S7} calculates distribution function for $\lambda*$ with an increasing number of trials. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2). Note the special case where there is no observation of the two species co-occurring, $n = 0$.  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.

@@

      As with the galler-natural enemy component (presented in the main text), we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}). We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component. These prior parameters were then used to estimate the posterior distribution.

      For species where $n=0$ (3,986/4,992 \emph{Salix}-galler pairs in our dataset), estimates for the mean and variance of $\lambda_{ij}$ can be calculated directly from the prior distribution (\emph{Appendix S6}). For the \emph{Salix}-galler network, these parameters were: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$; note that this mean is much lower than that obtained using a prior based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}. Note that, despite the intensive sampling in the~\ref{Kopelke2017} dataset, most \emph{Salix}-galler pairs were never observed co-occurring (3,986/4,992; Fig.~\ref{histograms}).

@@

      For species with $n>0$, the posterior distribution will depend on the values of $n$ and $k$. Here we are interested only in cases where $k = 0$. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. For a pair of species which co-occurred at all 374 sites and was never observed to interact, the distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$. As $n$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}). The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}).

      \begin{figure}[h!]
        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for $\lambda$ ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top) approaches zero and the 95\% credible interval (lines at top) narrows as sample size increases. Dashed lines indicate threshold probabilities of 0.1, 0.05, and 0.01.}
        \label{Salix_pdfs}
        \begin{center}
        \includegraphics*[width=.9\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
        \end{center}
        \end{figure}

@@

      Using the binary networks described above, we obtained prior parameters $\alpha$=2.51 and $\beta$=1.89 for the \emph{Salix}-galler component and $\alpha$=1.34, $\beta$=9.49 for the galler-natural enemy component of the network. We then calculated prior distributions using these parameters. For the \emph{Salix}-galler network, the prior distribution was: $\bar\lambda$=0.570, var($\lambda$)=0.056. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.124, var($\lambda$)=0.010. As with the results in the main text, we can update this prior distribution using observed co-occurrences. In the most extreme case where a pair of species co-occurred at all 374 sites and was never observed interacting, our distributions would become 
      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.

@@

      \begin{figure}[h!]
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component. This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
        \label{Salix_pdfs}
        \begin{center}
        \includegraphics*[width=.65\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
        \end{center}
        \end{figure}

@@

      \begin{figure}[h!]
        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network. In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrences was 0.364. All pairs of species therefore have $\lambda$\textless0.5.}
        \label{Salix_cdfs}
        \begin{center}
        \includegraphics[width=.65\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
        \end{center}
        \end{figure}

@@

  The following simple functions are implemented in the R language. They are 
  also provided as R code in a separate file.
  Priordata is the list of interaction frequencies from the prior 
  data, $n$ is the number of sites with observed co-occurrence of 
  species $i$ and $j$, and $k$ is the number of sites with an 
  observed interaction $ij$. When calculating the prior 
  distribution, both $n$ and $k$ are 0. In the main text we assume 100\%
  confidence in observed interactions and therefore consider only 
  cases where $k$=0. Only $n$ varies between species pairs.

>>>>

  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure (see Fig. 1, main text), we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty. We began by constructing 100 ``true" networks with 50 consumer species, 50 resource species, and a connectance of 0.1. We ensured that each network had at least one link per consumer and per resource. For each network, we calculated the mean number of links per consumer, mean number of links per resource, and nestedness (NODF) as described in the main text. For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).

  Taking each ``true" network as a starting point, we then applied process uncertainty. The probability $p_{ij}$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution. As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred. The number of co-occurrences, $n_{ij}$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive. The number of occurrences, $k_{ij}$, of each interaction was then drawn from a binomial distribution based on $n_{ij}$ and $p_{ij}$. If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network. As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network. For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF.

  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks. As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n_{ij}$, from a uniform distribution. We also randomly selected the probability, $p$, of detecting each interaction. To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10. We created 100 detection-filtered networks for each process-filtered network (10000 per true network). For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF. Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.

  With each additional layer of uncertainty, the number of consumers and resources included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs). The connectance and number of links per consumer and per resource decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests). The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types. Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001). We note that these tests may reflect the large number of detection-filtered webs generated by our simulation. A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network. This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system. It also highlights the sometimes unpredictable effects that this uncertainty can have on higher-order structures such as nestedness.

@@

        The absence of an interaction on a given day could be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling [($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$]. Note that some external factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

@@

        \begin{figure}[h!]
          \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species $i$ and $j$ cannot interact (i.e., $\lambda_{ij}=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k_{ij}$ and observed co-occurrances $n_{ij}$. The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{ij,MLE}=\frac{k_{ij}}{n_{ij}}$. Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k_{ij}=0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k_{ij}=0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
          Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n_{ij}$ times but never interacting ($k_{ij}=0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
          \label{upper_limits}
          \begin{center}
          \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
          % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
          \end{center}
          \end{figure}

@@

    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. Consider the case where a pair of species have been observed co-occurring $n_{ij}$ times, of which they have been observed to interact in $k_{ij}= 0$ cases. To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial. In this framework, the number of successes $k_{ij}$ over $n_{ij}$ trials will follow a binomial distribution:

@@

    \noindent The parameter $\lambda_{ij}$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
    The maximal likelihood estimate (MLE) of $\lambda_{ij}$ is straightforward to find given $k_{ij}$ and $n_{ij}$:

@@

    Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda_{ij}$ :

@@

    According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}). Since $\lambda_{ij}$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:

@@

   The beta-binomial distribution is a conjugate distribution of the binomial distribution. This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution. We can re-write the posterior distribution of $\lambda_{ij}$ as:

@@

    \noindent where the function $B$ is the beta function. The posterior distribution of $\lambda_{ij}$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.

    For interactions which were observed in at least one site ($k_{ij}$\textgreater$0$), we can set the poseterior probability to 1 as long as the risk of a false positive is low. That is, when constructing a metaweb we can assume that an interaction observed at least once is truly feasible. The case study presented in the main text refers to a plant-galler network compiled by rearing galling insects obtained from galls; in each case, the plant-galler interaction definitely occurred and we are confident in the identification of both species involved (see \emph{Appendix S4} for details). Where the risk of false positives is higher (e.g., plant-pollinator networks where an observed flower visitor may not actually provide a pollination service), it may not be appropriate to assume $\lambda_{ij}=0$ wherever $k_{ij}$\textgreater$0$. In such cases, we can model the posterior probabilities of observed interactions just as we do those that were not observed.

@@

      It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda_{ij}$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

      The \textbf{average} of $\lambda_{ij}$ is: 
          \begin{equation}
            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
            \label{mean}
          \end{equation}

@@

      The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n_{ij}=10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k_{ij}=3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\lambda_{ij,MLE} = 3/10 = 0.3$.

@@

        The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{ij,MLE}$ obtained from the observed data. We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{ij,MLE}$. With some simple R code (function ``calculate\_parameters", \emph{Appendix S7}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63. Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S7}), we find a prior $\bar\lambda_{ij}$=0.177 and var($\lambda_{ij}$)=0.026. Adding the observed data ($n_{ij}=10$, $k_{ij}=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda_{ij}$=0.256 and var($\lambda_{ij}$)=0.012. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance. We may also wish to calculate a credible interval (analogous to the frequentist confidence interval). This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S7}). In this case, a 95\% credible interval for $\bar\lambda_{ij}$ is (0.080, 0.491).

        Now, consider the case where the two species have never been observed interacting across $n_{ij}$ trials, i-e. $k_{ij}=0$. The question is then ``what is the probability that these two species do not interact''? Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda_{ij}=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda_{ij}\sim0$). We call this threshold probability $\lambda_{ij}*$. We then use the cumulative distribution function to estimate $P(\lambda_{ij}<\lambda_{ij}*|L=0,n)$ for different $n_{ij}$. The function ``samples\_for\_threshold" in \emph{Appendix S7} calculates distribution function for $\lambda_{ij}*$ with an increasing number of trials. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda_{ij}*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2). Note the special case where there is no observation of the two species co-occurring, $n_{ij}= 0$.  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.

@@

      As with the galler-natural enemy component (presented in the main text), we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species. We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component. These prior parameters were then used to estimate the posterior distribution.

      For species where $n_{ij}=0$ (3,986/4,992 \emph{Salix}-galler pairs in our dataset), estimates for the mean and variance of $\lambda_{ij}$ can be calculated directly from the prior distribution. For the \emph{Salix}-galler network, these parameters were: $\bar\lambda_{ij}$=0.028, var($\lambda_{ij}$)=8.60$\times$10$^{-5}$; note that this mean is much lower than that obtained using a prior based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}. Note that, despite the intensive sampling in the~\ref{Kopelke2017} dataset, most \emph{Salix}-galler pairs were never observed co-occurring (3,986/4,992; Fig.~\ref{histograms}).

@@

      For species with $n_{ij}>0$, the posterior distribution will depend on the values of $n_{ij}$ and $k_{ij}$. Here we are interested only in cases where $k_{ij}=0$. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. For a pair of species which co-occurred at all 374 sites and was never observed to interact, the distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$. As $n_{ij}$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}). The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}, \empH{Appendix S11}).

      \begin{figure}[h!]
        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species $i$ and $j$ that have not yet been observed interacting. Here we show posterior distributions for $\lambda_{ij}$ ranging from the prior distribution ($n_{ij}=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top) approaches zero and the 95\% credible interval (lines at top) narrows as sample size increases. Dashed lines indicate threshold probabilities of 0.1, 0.05, and 0.01.}
        \label{Salix_pdfs}
        \begin{center}
        \includegraphics*[width=.9\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
        \end{center}
        \end{figure}

@@

      Using the binary networks described above, we obtained prior parameters $\alpha$=2.51 and $\beta$=1.89 for the \emph{Salix}-galler component and $\alpha$=1.34, $\beta$=9.49 for the galler-natural enemy component of the network. We then calculated prior distributions using these parameters. For the \emph{Salix}-galler network, the prior distribution was: $\bar\lambda_{ij}$=0.570, var($\lambda_{ij}$)=0.056. The prior distribution for the galler-natural enemy network was: $\bar\lambda_{ij}$=0.124, var($\lambda_{ij}$)=0.010. As with the results in the main text, we can update this prior distribution using observed co-occurrences. In the most extreme case where a pair of species co-occurred at all 374 sites and was never observed interacting, our distributions would become 
      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.

@@

      \begin{figure}[h!]
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda_{ij}$ in each network ranging from the prior distribution ($n_{ij}=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component. This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
        \label{Salix_pdfs}
        \begin{center}
        \includegraphics*[width=.65\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
        \end{center}
        \end{figure}

@@

      \begin{figure}[h!]
        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network. In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrences was 0.364. All pairs of species therefore have $\lambda_{ij}$\textless0.5.}
        \label{Salix_cdfs}
        \begin{center}
        \includegraphics[width=.65\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
        \end{center}
        \end{figure}

@@

  The following simple functions are implemented in the R language. They are 
  also provided as R code in a separate file.
  Priordata is the list of interaction frequencies from the prior 
  data, $n_{ij}$ is the number of sites with observed co-occurrence of 
  species $i$ and $j$, and $k_{ij}$ is the number of sites with an 
  observed interaction $ij$. When calculating the prior 
  distribution, both $n_{ij}$ and $k_{ij}$ are 0. In the main text we assume 100\%
  confidence in observed interactions and therefore consider only 
  cases where $k_{ij}=0$. Only $n_{ij}$ varies between species pairs.
